Stochastic Variance-Reduced Policy Gradient

### 2018-06-27 poster/poster.tex
changed some colors

\colorlet{redp}{red!20} % vert S
\colorlet{greenp}{vert3!20} % vert S\usepackage[framemethod=tikz]{mdframed}
\colorlet{bluep}{blue!12} % vert S
\colorlet{blueg}{blue!70!green!90!white}
\definecolor{yellowp}{rgb}{0.99, 0.99, 0.59}
\colorlet{orangep}{orange!40}
\newcommand{\hl}[3][\fboxsep1pt]{{#1\colorbox{#2}{#3}}}%
%\newcommand{\hl}[2]{{\adjustbox{bgcolor=#1}{#2}}}%

\newcommand{\hlr}[1]{\hl{redp}{#1}}
\newcommand{\hlg}[1]{\hl{greenp}{#1}}
\newcommand{\hlb}[1]{\hl{bluep}{#1}}
\newcommand{\hlo}[1]{\hl{orangep}{#1}}
\newcommand{\hly}[1]{\hl{yellow!70!black!40!white}{#1}}
\newcommand{\hlblg}[1]{\hl{blue!75!green!20!white}{#1}}
\newcommand{\tikzhlblg}[1]{\tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=blue!75!green!20!white]{{#1}};}}
\newcommand{\tikzhly}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=yellow!70!black!50!white]{{#1}};}}
\newcommand{\tikzhlr}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=redp]{{#1}};}}
\newcommand{\tikzhlg}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=greenp]{{#1}};}}
\newcommand{\tikzhlb}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=bluep]{{#1}};}}

@@

%Reduce linespace in biblio
\setlength{\bibsep}{2pt}

@@

\noindent\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=bluep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlb{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hlr{frequent \textbf{SG}} with \\\hlg{rare \textbf{FG}} into a corrected gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{tcolorbox}
\end{minipage}\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=orangep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{tcolorbox}
\end{minipage}

\begin{center}
        Introducing the \enhance{SVRPG} estimator $\gradBlack{\vtheta}$:
\end{center}

@@

	\begin{enumerate}
	\item \textcolor{myblue}{\textbf{Unbiasedness:}} $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
	\item \textcolor{myblue}{\textbf{Vanishing variance:}} $\Var{\gradBlack{\vtheta}}\to0\:\:$ as $\:\:\vtheta\to\vtheta^*$
	\end{enumerate}
	\end{tcolorbox}
\end{minipage}
\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=yellow!70!black!40!white, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.2cm}
\hly{Importance weighting}

@@

\begin{itemize}
\item Constants ($\psi,\zeta,\xi$) depend only on \hlg{step size $\alpha$} and \hlg{epoch size $m$}
\item Theory dictates \hlr{very conservative} meta-parameters ($\alpha,m,N,B)$  to guarantee convergence
\end{itemize}
}

@@

\headerbox{Heuristics}{name=heuristics,column=3,span=1,row=0}{
\noindent
Heuristics can improve performance in practice
	\begin{itemize}
		\item \hlb{Step size:} \textbf{ADAM} to counteract gradient variance\\
		\dangersign \hspace*{.05cm} FG and SG variance have completely different magnitude $\rightarrow$ use two separate annealing schedules $\alpha_{FG}$ and $\alpha_{SG}$
		\item \hlb{Epoch size:} cut epoch when the effective step size becomes too small
		\begin{equation*}
			\frac{\alpha_{FG}}{N} > \frac{\alpha_{SG}}{B} \implies \textbf{new epoch}
		\end{equation*}
		\item \hlb{Normalized importance weights:} reduce variance at the price of introducing a small bias
		\item \hlb{Critic:} an orthogonal variance reduction technique from the \textbf{PG} literature
	\end{itemize}
}

>>>>

\colorlet{redp}{red!20} % vert S
\colorlet{greenp}{vert3!20} % vert S\usepackage[framemethod=tikz]{mdframed}
\colorlet{bluep}{blue!12} % vert S
\colorlet{blueg}{blue!70!green!90!white}
\definecolor{yellowp}{rgb}{0.93, 0.93, 0.42}
\colorlet{orangep}{orange!40}
\newcommand{\hl}[3][\fboxsep1pt]{{#1\colorbox{#2}{#3}}}%
%\newcommand{\hl}[2]{{\adjustbox{bgcolor=#1}{#2}}}%

\newcommand{\hlr}[1]{\hl{redp}{#1}}
\newcommand{\hlg}[1]{\hl{greenp}{#1}}
\newcommand{\hlb}[1]{\hl{bluep}{#1}}
\newcommand{\hlo}[1]{\hl{orangep}{#1}}
\newcommand{\hly}[1]{\hl{yellowp}{#1}}
\newcommand{\hlblg}[1]{\hl{blue!75!green!20!white}{#1}}
\newcommand{\tikzhlblg}[1]{\tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=blue!75!green!20!white]{{#1}};}}
\newcommand{\tikzhly}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=yellow!70!black!50!white]{{#1}};}}
\newcommand{\tikzhlr}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=redp]{{#1}};}}
\newcommand{\tikzhlg}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=greenp]{{#1}};}}
\newcommand{\tikzhlb}[1]{  \tikz[baseline]{\node[inner sep=2pt, anchor=base,fill=bluep]{{#1}};}}

@@

%Reduce linespace in biblio
\setlength{\bibsep}{1.5pt}

@@

\noindent\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=bluep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlb{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hlr{frequent \textbf{SG}} with \\\hlg{rare \textbf{FG}} into a \hly{corrected} gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{tcolorbox}
\end{minipage}\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=orangep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{tcolorbox}
\end{minipage}

\begin{center}
        Introducing the \large{\enhance{SVRPG}} estimator $\gradBlack{\vtheta}$:
\end{center}

@@

	\begin{enumerate}
	\item \textbf{Unbiasedness:} $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
	\item \textbf{Vanishing variance:} $\Var{\gradBlack{\vtheta}}\to0\:\:$ as $\:\:\vtheta\to\vtheta^*$
	\end{enumerate}
	\end{tcolorbox}
\end{minipage}
\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=yellowp, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.2cm}
\hly{Importance weighting}

@@

\begin{itemize}
\item Constants ($\psi,\zeta,\xi$) depend only on \hlg{step size $\alpha$} and \hly{epoch size $m$}
\item Theory dictates \hlr{very conservative} meta-parameters ($\alpha,m,N,B)$  to guarantee convergence
\end{itemize}
}

@@

\headerbox{Heuristics}{name=heuristics,column=3,span=1,row=0}{
\noindent
Heuristics can improve performance in practice
	\begin{itemize}
		\item \hlg{Step size:} \textbf{ADAM} to counteract gradient variance\\
		\dangersign \hspace*{.05cm} FG and SG variance have completely different magnitude $\rightarrow$ use two separate annealing schedules $\alpha_{FG}$ and $\alpha_{SG}$
		\item \hly{Epoch size:} cut epoch when the effective step size becomes too small
		\begin{equation*}
			\frac{\alpha_{FG}}{N} > \frac{\alpha_{SG}}{B} \implies \textbf{new epoch}
		\end{equation*}
		\item \hlb{Normalized importance weights:} reduce variance at the price of introducing a small bias
		\item \hlr{Critic:} an orthogonal variance reduction technique from the \textbf{PG} literature
	\end{itemize}
}
